Refining from the BON High-level Specification Language to the VHDL-AMS Hardware Description Language

### 2009-08-24 papers/BON_VHDL/paper.tex
minor correction

\subsection{Contracting and Refinement}
\emph{Contracting} is the definition, for each software element, 
of the associated semantic properties. BON use a full assertion mechanism, 
allowing analysts to specify not only the structure of a system but also its
semantics ( constraints and invariants of the expected results ). 
In VHDL-AMS \emph{simultaneous statement} represents analogue constraint of 
continuous-time waveform. In other words, analog kernel calculate quantities such 
that the constraints specified by the simultaneous statements are satisfied. 
We will agree that the constraint of waveform is nothing else than \emph{invariant}.
Another example of \emph{invariant} is conservation of energy law in which 
the summation of \arcoss quantities (\texttt{$\sum_{loop}$ across quatities =0}) 
around any loop equals zero and the summation of through 
quantities (\texttt{$\sum_{node}$ through quatities =0}) at any node equals zero. 
Moreover, any predefined (implicite) attribute in VHDL 
has defined pre(post) condition trought input(output) 
parameters and theirs constraints. Furthermore any subtype(subnature) 
represents restricted set of values from a base type(nature). 
The condition that determines which values are in the subtype(subnature)  
may be contracted by specifying characteristic predicate. 
For example, in typed $\lambda$ calculi, the VHDL-AMS subtype \lstinlinenc|bit| of 
\lstinlinenc|integer|, may be defined as \texttt{bit:=$\lambda$ n:nat.n < 2}. 
The corresponding informal and formal BON transformations are shown 
by the example below:
\input{bitbon}
Another advantage of BON is an easily-readable, English-based textual notation. 
The current IEEE standard VHDL-AMS language reference manual tries to define 
VHDL-AMS as well as possible in a descriptive way, explaining the 
semantics in English.\\
Therefore, on the basis of the above, BON is the obvious choice 
for the our \ST simulator.
\section{Mapping between VHDL-AMS and BON}

>>>>

\subsection{Contracting and Refinement}
\emph{Contracting} is the definition, for each software element, 
of the associated semantic properties. BON use a full assertion mechanism, 
allowing analysts to specify not only the structure of a system but also its
semantics ( constraints and invariants of the expected results ). 
In VHDL-AMS \emph{simultaneous statement} represents analogue constraint of 
continuous-time waveform. In other words, analog kernel calculate quantities such 
that the constraints specified by the simultaneous statements are satisfied. 
We will agree that the constraint of waveform is nothing else than \emph{invariant}.
Another example of \emph{invariant} is conservation of energy law in which 
the summation of \arcoss quantities (\texttt{$\sum_{loop}$ across quatities =0}) 
around any loop equals zero and the summation of through 
quantities (\texttt{$\sum_{node}$ through quatities =0}) at any node equals zero. 
Moreover, any predefined (implicite) attribute in VHDL 
has defined pre(post) condition trought input(output) 
parameters and theirs constraints. Furthermore any subtype(subnature) 
represents restricted set of values from a base type(nature). 
The condition that determines which values are in the subtype(subnature)  
may be contracted by specifying characteristic predicate. 
For example, in typed $\lambda$ calculi, the VHDL-AMS subtype \lstinlinenc|bit| of 
\lstinlinenc|integer|, may be defined as \texttt{bit:=$\lambda$ n:nat.n < 2}. 
The corresponding informal and formal BON transformations are shown 
by the example below:
\input{bitbon}
Another advantage of BON is an easily-readable, English-based textual notation. 
The current IEEE standard VHDL-AMS language reference manual tries to define 
VHDL-AMS as well as possible in a descriptive way, explaining the 
semantics in English.\\
Therefore, on the basis of the above, BON is the obvious choice 
for the \ST simulator.
\section{Mapping between VHDL-AMS and BON}
